Stochastic Convolutional Sparse Coding \\ Supplementary Material

### 2019-01-30 cvpr2019/rebuttal/egrebuttal.tex

\documentclass[10pt,twocolumn,letterpaper]{article}

\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}

% Include other packages here, before hyperref.

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}
\input{macro}

%%%%%%%%% PAPER ID  - PLEASE UPDATE
\def\cvprPaperID{3722} % *** Enter the CVPR Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

\begin{document}

%%%%%%%%% TITLE - PLEASE UPDATE
\title{Author Response for Stochastic Convolutional Sparse Coding}  % **** Enter the paper title here

\maketitle
\thispagestyle{empty}

\underline{Reviewer 1}

\textbf{Novelty:}
It should be emphasized that the proposed method is the first spatial-domain solver for CSC problems that outperforms all the other Fourier-domain solvers in terms of time both in batch mode and online mode. Solving CSC problem in spatial domain brings higher capabilities of handling arbitrary boundary conditions, additional regularization terms (also see response to reviewer 3: \textbf{comparisons}) those can not be handled in fourier domain and multi-layered structures, offering CSC model higher feasibility to wider applications.

\textbf{Algorithm:}
It is not reasonable to value an algorithm by its complexity, while it should be valued by its effectiveness and efficiency. Easing complicated problems is also a key motivation for conducting researches.

\underline{Reviewer 2}

\textbf{Specific questions:}

1. $\Filter_k \in \mathbb{R}^{D \times D}$ is a Toeplitz matrix for filter $\filter_k \in \mathbb{R}^{M}$, specifically,
%\begin{equation}\label{toeplitz}
% \Filter_k =
% \begin{bmatrix}
%    \filter_{k,1} \\
%    \filter_{k,2} & \filter_{k,1}\\
%    \vdots        & \filter_{k,2} & \filter_{k,1}\\
%    \filter_{k,M} & \vdots        & \filter_{k,2}\\
%                  & \filter_{k,M} & \vdots       \\
%                  &               & \filter_{k,M} & \ddots\\
%                  &               &               &        & \ddots
%  \end{bmatrix}
%\end{equation}
\begin{equation}\label{toeplitz}
 \Filter_k =
 \begin{bmatrix}
    \filter_{k,1} \\
    \filter_{k,2} & \filter_{k,1}\\
    \vdots        & \filter_{k,2}\\
    \filter_{k,M} & \vdots       \\
                  & \filter_{k,M} & \ddots\\
                  &               &        & \ddots          
  \end{bmatrix}
\end{equation}
$\Filter = [\Filter_1, \dots, \Filter_K]$, therefore $\Filter$ has the size of $D \times DK$.

2. Problem (5) is solved according to all the data. For notation simplicity, we omit the notation for data samples. In line 145, we declare the equations are applied to all training samples for batch mode, and in line 351 we emphasize that the equations in online mode only applies to a portion of training samples. We will make this more clear in revised version.

3. For deriving updating rule (8), we can expand equation (7) as:
\begin{equation}
    \filter^t = \minimize{\filter} \frac{1}{2t} \filter^{\top} (\sum_{i=1}^{t}{(\Code^i)^{\top}\Code^i})\filter - \filter^{\top} (\sum_{i=1}^{t}{(\Code^i)^{\top}\signal^i})
\end{equation}
Let $\surC^t = \frac{1}{t}\sum_{i=1}^{t}{(\Code^i)^{\top}\Code^i}$ and $\surB^t = \frac{1}{t} \sum_{i=1}^{t}{(\Code^i)^{\top}\signal^i}$, then we obtain equation (9), and the updating rule (8) is obvious.

\underline{Reviewer 3}

\textbf{Sparsity:}
We have demonstrated the sparsity in the figure 4 of supplementary material, which states that on average the codes has $0.18\%$ non-zero elements for 100 filters. It also shows that using over-complete dictionary leads to $8\% - 10\%$ reduction on the non-zero elements and achieves significantly improved representation ability.

\textbf{Connections:}
The connections between section 2 and the proposed method can be understood from 2 aspects. The first two points in section 2 contributes to the first motivation. CSC model is an overparameterized model, and the sparsity property of the codes can hardly be exploited if solving the problem in fourier domain. The third point accounts for the second motivation that the dimension size of updating dictionary step is $D$ when solving it in fourier domain, instead of $M$ in spatial domain ($M \ll D$).

\textbf{PSNR:}
PSNR is the peak signal-to-noise ratio, measuring the difference between the reconstructed signal and the original one. We will explain it in the revised version.

\textbf{Parameter:}
The parameter sensitivity in CSC model has been extensively studied in Wohlberg et al.. We are not indented to re-report the parameter sensitivity.

\textbf{Comparisons:}
The comparisons between (3)(Choudhury et al.) and (4)(Degraux et al.) are not applicable because (3) distributes the data to multiple machines to ease the memory issue, while it stills has the heavy computational burden. The proposed single-core program is fair to compare with single-core implementations. (4) formulates the multimodal image reconstruction into the CSC model, and uses the basic coordinate descent algorithm to solve the problem in spatial domain (which are known to have poor runtime performance) because the multimodal image formation model is not convolution based. We emphasize that our proposed strategy can be perfectly aligned with this types of problem and achieve roughly one magnitude speedup (also see response to reviewer 1).

To achieve the final convergence, (2)(Papyan et al.) requires about $1.5 \times$ runtime over the presented fourier-domain solver (Heide et al.), that is to say our proposed SBCSC can run $3 \times$ faster than (2) ((2) needs over 300 iterations to converge while Heide et al. and ours SBCSC need only 12-14 iterations). We will add the convergence comparison with (2) in supplementary. The execution time of ours SOCSC is comparable to the reported results in (1)(Wang et al.), roughly $70-80$ seconds to process 10 images in fruit and city dataset, we will add the comparison in revised version. Notice that (1) runs on GPUs and introduces base filters to represent the original filters, making the problem more complicated. All the discussions will be added.

We emphasize that none of the precedent work represent the importance of the over-complete dictionaries learned in CSC model, and we have shown that they are essential in image reconstruction tasks.

%{\small
%\bibliographystyle{ieee}
%\bibliography{egbib}
%}

\end{document}

### 2019-02-07 cvpr2019/rebuttal/egrebuttal.tex

%%%%%%%%% TITLE - PLEASE UPDATE
\title{Author Response for Stochastic Convolutional Sparse Coding}  % **** Enter the paper title here

\maketitle
\thispagestyle{empty}

\underline{Reviewer 1}

\textbf{Novelty:} It should be emphasized that the proposed method is
the first spatial-domain solver for CSC problems that outperforms all
the other Fourier-domain solvers in terms of time both in batch mode
and online mode. Solving CSC problem in spatial domain brings higher
capabilities of handling arbitrary boundary conditions, additional
regularization terms (also see response to reviewer 3:
\textbf{comparisons}) those can not be handled in the Fourier domain
and multi-layered structures, offering CSC model higher feasibility to
wider applications.

\textbf{Simplicity:} We believe an algorithm should be judged based on
by its effectiveness and efficiency, now on how complicated it is. In
fact, simplicity is a virtue, and simplifying complicated problems is
also a key motivation for conducting research.

@@

\underline{Reviewer 2}

\textbf{Specific questions:}

1. $\Filter_k \in \mathbb{R}^{D \times D}$ is a Toeplitz matrix for filter $\filter_k \in \mathbb{R}^{M}$, specifically,
%\begin{equation}\label{toeplitz}
% \Filter_k =
% \begin{bmatrix}
%    \filter_{k,1} \\
%    \filter_{k,2} & \filter_{k,1}\\
%    \vdots        & \filter_{k,2} & \filter_{k,1}\\
%    \filter_{k,M} & \vdots        & \filter_{k,2}\\
%                  & \filter_{k,M} & \vdots       \\
%                  &               & \filter_{k,M} & \ddots\\
%                  &               &               &        & \ddots
%  \end{bmatrix}
%\end{equation}
\begin{equation}\label{toeplitz}
 \Filter_k =
 \begin{bmatrix}
    \filter_{k,1} \\
    \filter_{k,2} & \filter_{k,1}\\
    \vdots        & \filter_{k,2}\\
    \filter_{k,M} & \vdots       \\
                  & \filter_{k,M} & \ddots\\
                  &               &        & \ddots
  \end{bmatrix}
\end{equation}
$\Filter = [\Filter_1, \dots, \Filter_K]$, therefore $\Filter$ has the size of $D \times DK$.

2. Problem (5) is solved according to all the data. For notational simplicity, we omit the notation for data samples. In line 145, we declare the equations are applied to all training samples for batch mode, and in line 351 we emphasize that the equations in online mode only applies to a portion of training samples. We will make this more clear in revised version.

@@

3. For deriving updating rule (8), we can expand equation (7) as:
\begin{equation}
    \filter^t = \minimize{\filter} \frac{1}{2t} \filter^{\top} (\sum_{i=1}^{t}{(\Code^i)^{\top}\Code^i})\filter - \filter^{\top} (\sum_{i=1}^{t}{(\Code^i)^{\top}\signal^i})
\end{equation}
Let $\surC^t = \frac{1}{t}\sum_{i=1}^{t}{(\Code^i)^{\top}\Code^i}$ and $\surB^t = \frac{1}{t} \sum_{i=1}^{t}{(\Code^i)^{\top}\signal^i}$, then we obtain equation (9), and the updating rule (8) is obvious.

\underline{Reviewer 3}

\textbf{Sparsity:}
We have demonstrated the sparsity in the Figure 4 of supplementary material, which states that on average the codes has $0.18\%$ non-zero elements for 100 filters. It also shows that using over-complete dictionary leads to $8\% - 10\%$ reduction on the non-zero elements and achieves significantly improved representation ability.

\textbf{Connections:}
The connections between section 2 and the proposed method can be
understood from 2 aspects. The first two points in Section 2
contribute to the first motivation. CSC model is an overparameterized
model, and the sparsity property of the codes can hardly be exploited
if solving the problem in the Fourier domain. The third point accounts
for the second motivation that the dimension size of updating
dictionary step is $D$ when solving it in the Fourier domain, instead of $M$ in spatial domain ($M \ll D$).

@@

\textbf{PSNR:}
PSNR is the peak signal-to-noise ratio, measuring the difference between the reconstructed signal and the original one. We will explain it in the revised version.

\textbf{Parameter:}
The parameter sensitivity in CSC model has been extensively studied in Wohlberg et al.. We are not indented to re-report the parameter sensitivity.

\textbf{Comparisons:} The comparisons between (3)(Choudhury et al.)
and (4)(Degraux et al.)  are not applicable. (3) is focused on memory
efficiency by splitting a large problem into smaller chunks, which can
be solved sequentially on one node or in parallel on multiple
nodes. This splitting however introduces additional computational
overhead compared to Heide et al, which we compare against. (4) formulates the multimodal image reconstruction into the CSC model, and uses the basic coordinate descent algorithm to solve the problem in spatial domain (which are known to have poor runtime performance) because the multimodal image formation model is not convolution based. We emphasize that our proposed strategy can be perfectly aligned with this types of problem and achieve roughly one magnitude speedup (also see response to reviewer 1).

To achieve the final convergence, (2)(Papyan et al.) requires about $1.5 \times$ runtime over the presented Fourier-domain solver (Heide et al.), that is to say our proposed SBCSC can run $3 \times$ faster than (2) ((2) needs over 300 iterations to converge while Heide et al. and ours SBCSC need only 12-14 iterations). The execution time of ours SOCSC is comparable to the reported results in (1)(Wang et al.), roughly $70-80$ seconds to process 10 images in fruit and city dataset, we will add the comparison in revised version. Notice that (1) runs on GPUs and introduces base filters to represent the original filters, making the problem more complicated. These additional comparisons affirm the superiority of the proposed method. All the comparisons and discussions will be added.

### 2019-02-07 cvpr2019/rebuttal/egrebuttal.tex

\begin{document}

%%%%%%%%% TITLE - PLEASE UPDATE
\title{Author Response for Stochastic Convolutional Sparse Coding}  % **** Enter the paper title here

\maketitle
\thispagestyle{empty}

\underline{General comments}

\textbf{Convergence:} This work is application-oriented addressing limitations in existing methods, and explores new directions tackling the problem and achieves improved learning efficiency. The empirical convergence has been validated on multiple datasets, and the demonstrated efficiency offers broader potential research directions on CSC model those fit well with CVPR interests. We agree a theoretical analysis is desired for the proposed method, however, judging the work \textbf{only} by its theoretical guarantee is biased.

%The work should not only be valued by its theoretical guarantee, but also its experimental performance and contributions to this field that fit well with CVPR venue.

@@

\underline{Reviewer 1}

\textbf{Novelty:}
It should be emphasized that the proposed method is the first spatial-domain solver for CSC problem that outperforms existing Fourier-domain solvers in terms of time both in batch mode and online mode. Solving CSC problem in spatial domain brings higher capabilities of handling arbitrary boundary conditions, additional regularization terms those can not be handled in Fourier domain (also see response to reviewer 3: \textbf{comparisons}), offering CSC model higher feasibility to wider applications.

\textbf{Simplicity:} We believe an algorithm should be judged by its effectiveness and efficiency, not on how complicated it is. Simplicity is a virtue, and simplifying complicated problems is also a key motivation for conducting research.

%\textbf{Algorithm:}
%It is unfair to value an algorithm by its complexity, while it should be valued by its effectiveness and efficiency. Easing complicated problems is also a key motivation for conducting researches.

@@

\underline{Reviewer 2}

\textbf{Specific questions:}

1. $\Filter_k \in \mathbb{R}^{D \times D}$ is a Toeplitz matrix for filter $\filter_k \in \mathbb{R}^{M}$,
%\begin{equation}\label{toeplitz}
% \Filter_k =
% \begin{bmatrix}
%    \filter_{k,1} \\
%    \filter_{k,2} & \filter_{k,1}\\
%    \vdots        & \filter_{k,2} & \filter_{k,1}\\
%    \filter_{k,M} & \vdots        & \filter_{k,2}\\
%                  & \filter_{k,M} & \vdots       \\
%                  &               & \filter_{k,M} & \ddots\\
%                  &               &               &        & \ddots
%  \end{bmatrix}
%\end{equation}
\begin{equation}\label{toeplitz}
 \Filter_k =
 \begin{bmatrix}
    \filter_{k,1} \\
    \filter_{k,2} & \filter_{k,1}\\
    \vdots        & \filter_{k,2}\\
    \filter_{k,M} & \vdots       \\
                  & \filter_{k,M} & \ddots
  \end{bmatrix} \nonumber
\end{equation}
$\Filter = [\Filter_1, \dots, \Filter_K]$, therefore $\Filter$ has the size of $D \times DK$.

2. Problem (5) is solved according to all data. For notational simplicity, we omit the notation for data samples. In line 145, we declare the equations are applied to all training samples for batch mode, and in line 351 we emphasize that the equations in online mode only applies to a portion of the samples. We will make this more clear in revised version.

3. In order to deriving updating rule (8), we can expand equation (7) as:
%\begin{equation}
$\filter^t = \minimize{\filter} \frac{1}{2t} \filter^{\top} (\sum_{i=1}^{t}{(\Code^i)^{\top}\Code^i})\filter - \frac{1}{t}\filter^{\top} (\sum_{i=1}^{t}{(\Code^i)^{\top}\signal^i})$ . %\nonumber
%\end{equation}
Let $\surC^t = \frac{1}{t}\sum_{i=1}^{t}{(\Code^i)^{\top}\Code^i}$ and $\surB^t = \frac{1}{t} \sum_{i=1}^{t}{(\Code^i)^{\top}\signal^i}$, then we obtain equation (9), and the rule (8) is obvious for a recursive computation.

@@

\underline{Reviewer 3}

\textbf{Sparsity:}
We have demonstrated the sparsity in Figure 4 of supplementary material, which states that on average the codes has $0.18\%$ non-zero elements for 100 filters. It also shows that using over-complete dictionary leads to $8\% - 10\%$ reduction on the non-zero elements and achieves significantly improved representation ability.

\textbf{Connections:}
The connections between section 2 and the proposed method can be understood from 2 aspects. The first two points in section 2 contributes to the first motivation. CSC model is an overparameterized model, and the sparsity property of the codes can hardly be exploited if solving the problem in Fourier domain. The third point accounts for the second motivation that the dimension size of updating dictionary step is $D$ when solving it in Fourier domain, instead of $M$ in spatial domain ($M \ll D$).

@@

\textbf{PSNR:}
PSNR is the peak signal-to-noise ratio, measuring the difference between the reconstructed signal and the original one. We will explain it in the revised version.

\textbf{Parameter:}
The parameter sensitivity in CSC model has been extensively studied in Wohlberg et al. 2016. If the reviewer asks for, we will add it in supplement.

\textbf{Comparisons:}
The comparisons with (3)(Choudhury et al. ICCV 2017) and (4)(Degraux et al. ICIP 2017) are not applicable. (3) focuses on memory
efficiency by splitting a large problem into smaller chunks, which can be solved sequentially on one node or in parallel on multiple
nodes. This splitting however introduces additional computational overhead compared to Heide et al, which we compare against. (4) formulates the multimodal image reconstruction into the CSC model, and uses the basic coordinate descent algorithm to solve the problem in spatial domain (which are known to have poor runtime performance) because the multimodal imaging model is not convolution based. We emphasize that our proposed strategy can be perfectly aligned with this types of problem and achieve roughly one magnitude speedup (also see response to reviewer 1).

% because (3) distributes the data to multiple machines to ease the memory issue, while it stills has the heavy computational burden. The proposed single-core program is fair to compare with single-core implementations.

To achieve the final convergence, (2)(Papyan et al. ICCV 2017) requires $1.5 \times$ runtime over the compared Fourier-domain solver (Heide et al.), namely ours SBCSC can run $3 \times$ faster than (2) ((2) needs over 300 iterations to converge while Heide et al. and ours need only 12-14 iterations). The runtime of ours SOCSC is \textbf{comparable} to the reported results in (1)(Wang et al. ICML 2018), roughly $70$ seconds to process the fruit and city dataset. \textbf{Notice that} (1) runs on GPUs and introduces base filters to represent the original filters, making the problem more complicated. These additional comparisons \textbf{affirm the superiority} of the proposed method. All the comparisons and discussions will be added.

We emphasize that none of the precedent work represent the importance of the over-complete dictionary learned in CSC model, and we have shown that they play an important role in image reconstruction tasks.

### 2019-08-19 VMV19/CSCmodel.tex
add directory

\section{Convolutional Sparse Coding (CSC)}
The dictionary learning problem for CSC problem has the form
\begin{equation}\label{eq:CSCmodel}
\begin{split}
    \mini{\filter,\code} & \frac{1}{2}\|\signal - \sum_{k=1}^{K} \filter_k * \code_k \|_2^2 + \lambda \sum_{k=1}^{K}\| \code_k \|_1 \\
    \text{subject to} & ~ \|\filter_k\|^2_2 \leq 1 ~~ \forall k \in \{1,\dots,K\},
\end{split}
\end{equation}
where $\signal \in \mathbb{R}^D$ is a $D$-dimensional signal or a
vectorized image\footnote{In this manuscript, we work on 2D images.},
$\filter_k \in \mathbb{R}^M$ is the $k$-th dictionary, $\code_k\in
\mathbb{R}^D$ is the sparse code associated with that dictionary,
$\lambda>0$ is a sparsity inducing penalty parameter, $K$ is the
number of dictionary filters, and $*$ is the convolution operator. The
above model will be applied to all the training images
$\signal\in\mathbb{X}$.

>>>>

\section{Convolutional Sparse Coding (CSC)} \label{CSCmodel}
The dictionary learning problem for CSC problem has the form
\begin{equation}\label{eq:CSCmodel}
\begin{split}
    \mini{\filter,\code} & \frac{1}{2}\|\signal - \sum_{k=1}^{K} \filter_k * \code_k \|_2^2 + \lambda \sum_{k=1}^{K}\| \code_k \|_1 \\
    \text{subject to} & ~ \|\filter_k\|^2_2 \leq 1 ~~ \forall k \in \{1,\dots,K\},
\end{split}
\end{equation}
where $\signal \in \mathbb{R}^D$ is a $D$-dimensional signal or a
vectorized image,
$\filter_k \in \mathbb{R}^M$ is the $k$-th dictionary, $\code_k\in
\mathbb{R}^D$ is the sparse code associated with that dictionary,
$\lambda>0$ is a sparsity inducing penalty parameter, $K$ is the
number of dictionary filters, and $*$ is the convolution operator. The
above model will be applied to all the training images
$\signal\in\mathbb{X}$.

### 2019-08-19 VMV19/Conclusion.tex
add directory

\section{Conclusions}
In this work, we present a novel stochastic subsampling strategy for
solving the CSC problem in the spatial domain. This method
significantly improves the runtime performance over the prior
frequency-domain solvers, which applies to both batch mode and
online-learning mode.  The proposed algorithm, for the first time,
demonstrates the feasibility that tackling the CSC problem in spatial
domain while still holding, or even improving the runtime
efficiency. Since the subproblem of updating the code is a highly
sparse LASSO, other specific optimization strategies can be applied to
further accelerate the computation, for instance the idea proposed
in~\cite{johnson2017stingycd}, which solves the LASSO problem by
coordinate descent and skips unnecessary updates using the method of
safe screening~\cite{ghaoui2012Swfe}. It is worth emphasizing that
Fourier-domain methods cannot benefit from these kinds of speedup
strategies.

In the future, alternative subsampling strategies can be studied to
improve learning efficiency. Instead of employing uniform subsampling
strategy, for instance one could employ an importance or correlation
based sampling strategy that considers the inter-dependency between the
signals and the sparse codes.

We have also shown the capability of the developed online algorithm to
learn representative and meaningful over-complete dictionary from
arbitrary large datasets, and the availability of the dictionary is
further verified by the application of image inpainting. It can be
foreseen that this capability has widespread applications in audio
and image related tasks, and higher dimensional signal processing. The
source code for SBCSC and SOCSC is attached in the supplement for
reference.

>>>>

\section{Conclusions}
In this work, we present a novel stochastic subsampling strategy for
solving the CSC problem in the spatial domain. This method exploits 
the sparsity of the \changed{over-parameterized} model and improves the runtime performance over the prior
frequency-domain solvers, which applies to both batch mode and
online-learning mode.  The proposed algorithm, for the first time,
demonstrates the feasibility that tackling the CSC problem in spatial
domain while still holding, or even improving the runtime
efficiency. Since the subproblem of updating the code is a highly
sparse LASSO, other specific optimization strategies can be applied to
further accelerate the computation, for instance the idea proposed
in~\cite{johnson2017stingycd}, which solves the LASSO problem by
coordinate descent and skips unnecessary updates using the method of
safe screening~\cite{ghaoui2012Swfe}. It is worth emphasizing that
Frequency-domain methods cannot benefit from these kinds of speedup
strategies.

%In the future, alternative subsampling strategies can be studied to
%improve learning efficiency. Instead of employing uniform subsampling
%strategy, for instance one could employ an importance or correlation
%based sampling strategy that considers the inter-dependency between the
%signals and the sparse codes.

We have also shown the capability of the developed online algorithm to
learn representative and meaningful over-complete dictionary from
arbitrary large datasets, and the availability of the dictionary is
further verified by the application of image inpainting. It can be
foreseen that this capability has widespread applications in audio
and image related tasks, and higher dimensional signal processing.

### 2019-08-19 VMV19/Introduction.tex
add directory

Of course this convolutional approach is also at the heart of many deep
learning-based methods in the form of
CNNs~\cite{lecun1998gradient,kavukcuoglu2010learning,krizhevsky2012imagenet},
which have in recent years been extraordinarily successful for a broad
range of high-level image understanding applications. However, while
CNNs generally are used in a {\em supervised} setting and produce {\em
  discriminative}, task-specific models, CSC is {\em unsupervised} and
produces {\em generative} models that easily transfer between tasks.

@@

{\bfseries Contributions.} We mainly make three contributions in this
work. First, we introduce a randomization strategy for the CSC
model and solve the entire problems in spatial domain. We demonstrate
that the proposed stochastic spatial-domain solver, with a reasonably
selected subsampling rate, outperforms the state-of-the-art
frequency-domain solvers with regard to computing efficiency. We then
formulate an online-learning version of the proposed algorithm, and
show dramatic runtime improvement over current online CSC methods,
while producing comparable outcomes. Finally, we demonstrate the
capability to learn the over-complete dictionary from thousands of
images, and analyze the effectiveness of the learned over-complete
dictionary for a number of reconstruction tasks.

>>>>

\changed{This convolutional approach is also at the heart of many deep
learning-based methods in the form of
CNNs~\cite{lecun1998gradient,kavukcuoglu2010learning,krizhevsky2012imagenet},
which have in recent years been extraordinarily successful for a broad
range of high-level image understanding applications. However, while
CNNs generally are used in a {\em supervised} setting and produce {\em
  discriminative}, task-specific models, CSC is {\em unsupervised} and
produces {\em generative} models that can easily be transferred between tasks.}

@@

{\bfseries Contributions.} \changed{We mainly make three contributions in this
work. First, we introduce a randomization strategy for the CSC
model and solve the entire problems in the spatial domain. We demonstrate
that the proposed stochastic spatial-domain solver, with a reasonably
selected subsampling rate, outperforms the state-of-the-art
frequency-domain solvers with regard to computing efficiency. Secondly, we
formulate an online-learning version of the proposed algorithm, and
show dramatic runtime improvement over current online CSC methods,
while producing comparable outcomes. Finally, we demonstrate the
capability to learn the meaningful over-complete dictionary from thousands of
images, and analyze the effectiveness of the learned over-complete
dictionary for a number of reconstruction tasks.}
